
```{r setup}
source("dependencies.R")
```

```{r}
# data1996 <- read_dta("data/GSS1996.dta")
data2004 <- read_dta("data/GSS2004.dta")
# data2014 <- read_dta("data/GSS2014.dta")
```

On se limite pour l'instant aux données concernant l'année 2004.

# Recodages

## Outcomes

Les données proviennent du module Identité Nationale, pp.96-109 du questionnaire disponible ici : <https://gss.norc.org/content/dam/gss/get-documentation/pdf/quex/2004%20GSS%20V6.pdf>

Ce module a seulement été administré à 1215 personnes.

Une difficulté est que les variables retournées par haven sont mixtes : numériques pour les réponses effectives, textuelles pour les types de NAs. Or, il serait dommage d'agréger directement les NAs, car certaines correspondes à des réponses effectives, avec la modalité can't choose. Il faut plusieurs conversions successives pour bien récupérer cette dernière. On la traite comme une modalité neutre, les échelles de Likert à 4 modalités passant ainsi à 5. On en profite pour standardiser les valeurs en les centrant sur 0, ainsi que les labels. On obtient deux nouvelles variables : l'une numérique correspondant à un score, l'autre factorielle.

```{r}
# Score recoding
mods <- c(-2:2)
lbls <- c('Not at all', 'Not very much', 'Can\'t choose', 'Somewhat / fairly', 'Very much')

# B&M recoding
# mods <- c(1,2,NA_real_,3,4)
# lbls <- c('Not at all', 'Not very much', 'Somewhat / fairly', 'Very much')
```

### Q.2

How close do you feel to...

a.  Your town or city

b.  Your state

c.  America

d.  North America

B&M retiennent n'utilisent pas les items a (clsetown), b (clsestat) et d (clsenoam).

```{r}
# Variables
q2_vars <- c('clsetown', 'clsestat', 'clseusa', 'clsenoam')
q2_vars_n <- paste0(q2_vars, "_n")

# Labels
# q2_lbls <- c('Not close at all', 'Not very close', 'Can\'t choose', 'Close', 'Very close') # original
q2_lbls <- lbls # standardized

data2004 <- data2004 %>%
  mutate(across(all_of(q2_vars), 
                ~ as_factor(.)
  )) %>%
  mutate(across(all_of(q2_vars), 
                ~ case_when(
                  . == 'VERY CLOSE' ~ mods[5],
                  . == 'close' ~ mods[4],
                  . == 'CANT CHOOSE' ~ mods[3],
                  . == 'NOT VERY CLOSE' ~ mods[2],
                  . == 'NOT CLOSE AT ALL' ~ mods[1],
                  TRUE ~ NA_real_),
                .names = '{.col}_n')) %>%
  mutate(across(all_of(q2_vars_n), 
                ~ factor(.,
                         levels = mods,
                         labels = q2_lbls),
                .names = "{stringr::str_replace(.col, '_n$', '')}_f"))
```

```{r}
# Labels
data2004 <- data2004 %>%
  set_variable_labels(
    clseusa_n = 'How close ... America',
    clsetown_n = 'How close ... your town or city',
    clsestat_n = 'How close ... your state',
    clsenoam_n = 'How close ... North America') %>%
  set_variable_labels(
    clseusa_f = 'How close ... America',
    clsetown_f = 'How close ... your town or city',
    clsestat_f = 'How close ... your state',
    clsenoam_f = 'How close ... North America')
```

### Q.3

Some people say the following things are important for being truly American. Others say they are not important. How important do you think each of the following is?

a.  To have been born in America

b.  To have American citizenship

c.  To have lived in America for most of one's life

d.  To be able to speak English

e.  To be a Christian

f.  To respect America's political institutions and laws

g.  To feel American 

h. To have American ancestry

B&M n'utilisent pas l'a modalité l'item h (amancstr).

```{r}
# Variables
q3_vars <- c('ambornin', 'amcit', 'amlived', 'amenglsh', 'amchrstn', 'amgovt', 'amfeel', 'amancstr')
q3_vars_n <- paste0(q3_vars, "_n")

# Labels
# q3_lbls <- c('Not important at all', 'Not very important', 'Can\'t choose', 'Fairly important', 'Very important') # originals
q3_lbls <- lbls # standardized

data2004 <- data2004 %>%
  mutate(across(all_of(q3_vars), 
                ~ as_factor(.)
  )) %>%
  mutate(across(all_of(q3_vars), 
                ~ case_when(
                  . == 'VERY IMPORTANT' ~ mods[5],
                  . == 'FAIRLY IMPORTANT' ~ mods[4],
                  . == 'NOT VERY IMPORTANT' ~ mods[2],
                  . == 'NOT IMPORTANT AT ALL' ~ mods[1],
                  . == 'CANT CHOOSE' ~ mods[3],
                  TRUE ~ NA_real_),
                .names = '{.col}_n')) %>%
  mutate(across(all_of(q3_vars_n), 
                ~ factor(.,
                         levels = mods,
                         labels = q3_lbls),
                .names = "{stringr::str_replace(.col, '_n$', '')}_f"))
```

```{r}
# Labels
data2004 <- data2004 %>%
  set_variable_labels(
    ambornin_n = 'How important ... to have been born in America',
    amcit_n = 'How important ... to have American citizenship',
    amlived_n = 'How important ... to have lived in America for most of one\'s life',
    amenglsh_n = 'How important ... to be able to speak English',
    amchrstn_n = 'How important ... to be a Christian',
    amgovt_n = 'How important ... to respect America\'s political institutions and laws',
    amfeel_n = 'How important ... to feel American',
    amancstr_n = 'How important ... to have American ancestry') %>%
  set_variable_labels(
    ambornin_f = 'How important ... to have been born in America',
    amcit_f = 'How important ... to have American citizenship',
    amlived_f = 'How important ... to have lived in America for most of one\'s life',
    amenglsh_f = 'How important ... to be able to speak English',
    amchrstn_f = 'How important ... to be a Christian',
    amgovt_f = 'How important ... to respect America\'s political institutions and laws',
    amfeel_f = 'How important ... to feel American',
    amancstr_f = 'How important ... to have American ancestry')
```

### Q.4

How much do you agree or disagree with the following statements?

a.  I would rather be a citizen of America than of any other country in the world

b.  There are some things about America today that make me feel ashamed of America

c.  The world would be a better place if people from other countries were more like the Americans

d.  Generally speaking, America is a better country than most other countries

e.  People should support their country even if the country is in the wrong.

f.  When my country does well in international sports, it makes me proud to be American

g.  I am often less proud of America than I would like to be

B&M n'utilisent pas les items f (amsports) et g (lessprd).

```{r}
# Variables
q4_vars <- c('amcitizn', 'amshamed', 'belikeus', 'ambetter', 'ifwrong', 'amsports', 'lessprd')
q4_vars_n <- paste0(q4_vars, "_n")

# Labels
# q4_lbls <- c('Strongly disagree', 'Disagree', 'Neither agree nor disagree', 'Agree', 'Strongly agree') # original
q4_lbls <- lbls # standardized

data2004 <- data2004 %>%
  mutate(across(all_of(q4_vars), 
                ~ as_factor(.)
  )) %>%
  mutate(across(all_of(q4_vars), 
                ~ case_when(
                  . == 'STRONGLY AGREE' ~ mods[5],
                  . == 'agree' ~ mods[4],
                  . == 'NEITHER AGREE NOR DISAGREE' ~ mods[3],
                  . == 'disagree' ~ mods[2],
                  . == 'STRONGLY DISAGREE' ~ mods[1],
                  . == 'CANT CHOOSE' ~ mods[3],
                  TRUE ~ NA_real_),
                .names = '{.col}_n')) %>%
  mutate(across(all_of(q4_vars_n), 
                ~ factor(.,
                         levels = mods,
                         labels = q4_lbls),
                .names = "{stringr::str_replace(.col, '_n$', '')}_f"))
```

```{r}
# Labels
data2004 <- data2004 %>%
  set_variable_labels(
    amcitizn_n = 'I would rather be a citizen of America than of any other country in the world',
    belikeus_n = 'The world would be a better place if people from other countries were more like the Americans',
    ambetter_n = 'Generally speaking, America is a better country than most other countries',
    ifwrong_n = 'People should support their country even if their country is in the wrong',
    amshamed_n = 'There are some things about America today that make me feel ashamed of America',
    amsports_n = 'When my country does well in international sports, it makes me proud to be American',
    lessprd_n = 'I am often less proud of America than I would like to be') %>%
  set_variable_labels(
    amcitizn_f = 'I would rather be a citizen of America than of any other country in the world',
    belikeus_f = 'The world would be a better place if people from other countries were more like the Americans',
    ambetter_f = 'Generally speaking, America is a better country than most other countries',
    ifwrong_f = 'People should support their country even if their country is in the wrong',
    amshamed_f = 'There are some things about America today that make me feel ashamed of America',
    amsports_f = 'When my country does well in international sports, it makes me proud to be American',
    lessprd_f = 'I am often less proud of America than I would like to be')
```

### Q.5

How proud are you of America in each of the following?

a.  The way democracy works

b.  Its political influence in the world

c.  America's economic achievements

d.  Its social security system

e.  Its scientific and technological achievements

f.  Its achievements in sports

g.  Its achievements in the arts & literature

h.  America's armed forces

i.  Its history

j.  Its fair and equal treatment of all groups in society

B&M utilisent tous les items.

```{r}
# Variables
q5_vars = c('proudsss', 'proudgrp', 'proudpol', 'prouddem', 'proudeco', 'proudspt', 'proudart', 'proudhis', 'proudmil', 'proudsci')
q5_vars_n <- paste0(q5_vars, "_n")

# Labels
# q5_lbls <- c('Not proud at all', 'Not very proud', 'Can\'t choose', 'Somewhat proud', 'Very pround') # original
q5_lbls <- lbls # standardized

data2004 <- data2004 %>%
  mutate(across(all_of(q5_vars), 
                ~ as_factor(.)
  )) %>%
  mutate(across(all_of(q5_vars), 
                ~ case_when(
                  . == 'VERY PROUD' ~ mods[5],
                  . == 'SOMEWHAT PROUD' ~ mods[4],
                  . == 'NOT VERY PROUD' ~ mods[2],
                  . == 'NOT PROUD AT ALL' ~ mods[1],
                  . == 'CANT CHOOSE' ~ mods[3],
                  TRUE ~ NA_real_),
                .names = '{.col}_n')) %>%
  mutate(across(all_of(q5_vars_n), 
                ~ factor(.,
                         levels = mods,
                         labels = q5_lbls),
                .names = "{stringr::str_replace(.col, '_n$', '')}_f"))
```

```{r}
# Labels
data2004 <- data2004 %>%
  set_variable_labels(
    prouddem_n = 'How proud ... the way democracy works',
    proudpol_n = 'How proud ... its political influence in the world',
    proudeco_n = 'How proud ... America\'s economic achievements',
    proudsss_n = 'How proud ... its social security system',
    proudsci_n = 'How proud ... its scientific and technological achievements',
    proudspt_n = 'How proud ... its achievements in sports',
    proudart_n = 'How proud ... its achievements in the arts & literature',
    proudmil_n = 'How proud ... America\'s armed forces',
    proudhis_n = 'How proud ... its history',
    proudgrp_n = 'How proud ... its fair and equal treatment of all groups in society') %>% 
  set_variable_labels(
    prouddem_f = 'How proud ... the way democracy works',
    proudpol_f = 'How proud ... its political influence in the world',
    proudeco_f = 'How proud ... America\'s economic achievements',
    proudsss_f = 'How proud ... its social security system',
    proudsci_f = 'How proud ... its scientific and technological achievements',
    proudspt_f = 'How proud ... its achievements in sports',
    proudart_f = 'How proud ... its achievements in the arts & literature',
    proudmil_f = 'How proud ... America\'s armed forces',
    proudhis_f = 'How proud ... its history',
    proudgrp_f = 'How proud ... its fair and equal treatment of all groups in society')
```

## Poids de sondage

```{r}
data2004 <- data2004 %>%
  mutate(wgt = as.numeric(wtssnr)) %>%
  set_variable_labels(wgt = 'survey_weights')
```

## Contrôles

### Âge

```{r}
data2004 <- data2004 %>%
  mutate(
    age_n = as.numeric(age),
    age_f = cut(
      age, 
      breaks = c(-Inf, 25, 40, 55, 70, Inf),
      labels = c('< 25 yo', '25-40 yo', '40-55 yo','55-70 yo', '>70 yo'),
      right = FALSE)) %>%
  set_variable_labels(
    age_n = 'Age',
    age_f = 'Age')
```

### Sexe

```{r}
data2004 <- data2004 %>%
  mutate(sex = factor(
      case_when(
        sex == 1 ~ 1,
        sex ==  2 ~ 0),
      levels = 0:1, 
      labels = c('F', 'M'))) %>%
  set_variable_labels(sex = "Sex")
```

### Race

La variable race comprend seulement 3 modalités : white / black / other. La variable ethnic est beaucoup plus détaillée, avec 45 modalités. B&M l'utilisent pour ajouter une modalité hispanc à la variable race, à partir des 2 modalités suivantes : mexico (17) / puerto rico (22) / other spanish (38).

```{r}
data2004 <- data2004 %>%
  mutate(race_f = factor(
      case_when(
        ethnic %in% c(17, 22, 38) ~ 3,
        race == 1 ~ 1,
        race == 2 ~ 2,
        race == 3 ~ 4,
        TRUE ~ NA_real_),
      levels = 1:4, 
      labels = c('White', 'Black', 'Hispanic', 'Other race'))) %>%
  set_variable_labels(race_f = "Race")
```

On a repris l'approche de B&M, qui fait primer l'ethnicité sur la race. Elle est discutable, car parmi les 185 personnes déclarant une ethnicité hispanique, 108 se déclarent de race blanche ou noire...

```{r eval=FALSE}
sum(data2004$ethnic %in% c(17, 22, 38), na.rm = TRUE)
sum(data2004$ethnic %in% c(17, 22, 38) & data2004$race %in% c(1,2), na.rm = TRUE)

sum(is.na(data2004$race))
sum(is.na(data2004$race_f))
```

### Éducation

```{r}
data2004 <- data2004 %>%
  mutate(
    educ_n = as.numeric(educ),
    educ_f = cut(
      educ, 
      breaks = c(-Inf, 12, 16, 17, Inf),
      labels = c('< High school', 'High school or some college', 'Bachelor', 'Advanced degree'),
      right = FALSE)) %>%
  set_variable_labels(
    educ_n = 'Education',
    educ_f = 'Education')
```

### Religion

```{r}
data2004 <- data2004 %>%
  mutate(reltrad_f = factor(
    case_when(
      # Mainline Protestant
      denom %in% c(12, 13, 14, 15, 20, 21, 23) |
        (denom %in% c(10, 11, 18, 28) & race == 2) |
        other %in% c(7, 14, 15, 21, 37, 38, 56, 78, 79, 85, 86, 87, 88, 98, 103, 104, 128, 133) |
        (other == 93 & race == 2) ~ 1,
      # Evangelical Protestant
      denom %in% c(32, 33, 34, 42) |
        (denom %in% c(10, 14, 15, 18, 23, 93) & race != 2) |
        other %in% c(2, 3, 5, 6, 9, 10, 12, 13, 16, 18, 20, 22, 24, 26, 27,
                     28, 29, 31, 32, 34, 35, 36, 41, 42, 43, 45, 47, 51, 52,
                     53, 55, 57, 63, 65, 66, 67, 68, 69, 76, 83, 84, 90, 91,
                     92, 94, 97, 100, 101, 102, 106, 107, 108, 109, 110, 111,
                     112, 115, 116, 117, 118, 120, 121, 122, 124, 125, 127,
                     129, 131, 132, 133, 134, 135, 138, 139, 140, 146) |
        (denom == 70 & attend >= 4 & attend != 9) ~ 2,
      # Black Protestant
      denom %in% c(22, 30, 31, 35, 38, 40, 41, 43, 48, 50) |
        (denom %in% c(11, 28) & race != 2) |
        other %in% c(1, 8, 19, 23, 25, 40, 44, 46, 48, 49, 50, 54, 
                     70, 71,72, 73, 81, 89, 96, 99, 105, 119, 148) ~ 3,
      # Other
      other %in% c(11, 17, 29, 30, 33, 58, 59, 60, 61, 62, 64, 74,
                   75, 80, 82, 95, 113, 114, 130, 136, 141, 145) ~ 6,
      # Catholic
      relig == 2 | other == 123 ~ 4,
      # Jewish
      relig == 3 ~ 5,
      # None
      relig == 4 ~ 0,
      # Other
      TRUE ~ 6),
    levels = 0:6, 
    labels = c('No religion', 'Mainline Protestant', 'Evangelical Protestant', 
               'Black Protestant', 'Catholic', 'Jewish', 'Other religion'))) %>%
  set_variable_labels(reltrad_f = 'Religion')

data2004 <- data2004 %>%
  mutate(religstr_f = factor(
    case_when(
      reliten == 1 ~ 1,
      reliten %in% c(2:4) ~ 0,
      TRUE ~ NA_real_),
    levels = c(0:1),
    labels = c('Strong', 'Not strong'))) %>%
  set_variable_labels(religstr_f = 'Religion affiliation')
```

### Revenus

```{r}
data2004 <- data2004 %>%
  mutate(
    realinc = as.numeric(realinc),
    realinc2004 = realinc * 1.72,
    lnrealinc2004 = log(realinc2004),
    realinc_f = cut(
      realinc, 
      breaks = c(-Inf, 10000, 20000, 30000, Inf),
      labels = c('< 10k', '10-20k', '20-30k','> 30k'),
      right = FALSE)) %>%
  set_variable_labels(
    realinc2004 = 'Family Income',
    lnrealinc2004 = 'Log of Family Income',
    realinc_f = 'Family Income')
```

### Identification partisane

```{r}
# B&M recoding
data2004 <- data2004 %>%
  mutate(party_f = factor(
      case_when(
        partyid == 0 ~ 1,
        partyid %in% c(1, 2) ~ 2,
        partyid == 3 ~ 3,
        partyid %in% c(4, 5) ~ 4,
        partyid == 6 ~ 5,
        partyid == 7 ~ 6,
        TRUE ~ NA_real_),
      levels = 1:6,
      labels = c("Strong Democrat", "Democrat", "Independent", "Republican", "Strong Republican", "Other party"))) %>%
  set_variable_labels(party_f = "Partishanship")

# Simpler recoding
data2004 <- data2004 %>%
  mutate(party_fs = factor(
      case_when(
        partyid %in% c(0:2) ~ 1,
        partyid %in% c(3,7) ~ 0,
        partyid %in% c(4:6) ~ -1,
        TRUE ~ NA_real_),
      levels = -1:1,
      labels = c("Republican", "Independent", "Democrat"))) %>%
  set_variable_labels(party_fs = "Partishanship")
```

### Lieu de naissance

```{r}
data2004 <- data2004 %>%
  mutate(born_usa = factor(
      case_when(
        born == 1 ~ 0,
        born ==  2 ~ 1,
        TRUE ~ NA_real_),
      levels = 0:1, 
      labels = c("Born in this country", "Not born in this country"))) %>%
  set_variable_labels(born_usa = "Was born in this country")
```

### Région

```{r}
data2004 <- data2004 %>%
  mutate(region_f = factor(
      case_when(
        region %in% 1:2 ~ 1,
        region %in% 3:4 ~ 2,
        region %in% 5:7 ~ 3,
        region == 8 ~ 4,
        region == 9 ~ 5,
        TRUE ~ NA_real_),
      levels = 1:5, 
      labels = c("Northeast", "Midwest", "South", "Mountain", "Pacific"))) %>%
  set_variable_labels(region_f = "Region")
```

# Valeurs manquantes

```{r}
q2_vars_f <- paste0(q2_vars, "_f")
q3_vars_f <- paste0(q3_vars, "_f")
q4_vars_f <- paste0(q4_vars, "_f")
q5_vars_f <- paste0(q5_vars, "_f")

base_outcomes <- c(q2_vars, q3_vars, q4_vars, q5_vars)
f_outcomes <- paste0(base_outcomes, "_f")
n_outcomes <- paste0(base_outcomes, "_n")
all_outcomes <- c(f_outcomes, n_outcomes)

f_controls <- c('sex', 'age_f', 'race_f', 'educ_f', 'born_usa', 'realinc2004', 'lnrealinc2004',
                'realinc_f', 'party_f', 'party_fs', 'religstr_f', 'reltrad_f', 'region_f')
n_controls <- c('age_n', 'educ_n', 'realinc2004', 'lnrealinc2004')
all_controls <- c(f_controls, n_controls)

all_vars <-c (all_outcomes, all_controls, 'wgt', 'id')
```

On élimine les enquêtés auxquels le module Identité nationale n'a pas été administré, plus un ayant répondu à seulement deux questions. On élimine aussi les variables non-utilisées.

```{r}
data2004_f <- data2004 %>%
  filter(!if_all(all_of(all_outcomes), is.na)) %>%
  filter(id != 769) %>%
  select(all_of(all_vars))
```

On étudie les NAs pour les outcomes : elles sont résiduelles, on pourra les imputer sans problème.

```{r}
data2004_f %>%
  summarise(across(all_of(f_outcomes), ~ sum(is.na(.)))) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "NAs") %>%
  filter(NAs > 0)

data2004_f %>% filter(if_any(all_of(f_outcomes), is.na)) %>%
  select(all_of(f_outcomes))
```

On étudie les NAs pour les contrôles : elles sont résiduelles aussi, sauf pour le revenu. On imputera aussi les deux variables concernées, mais il faudra s'en méfier par la suite.

```{r}
data2004_f %>%
  summarise(across(all_of(all_controls), ~ sum(is.na(.)))) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "NAs") %>%
  filter(NAs > 0)
```

On réalise l'imputation par knn.

```{r}
data2004_i <- data2004_f %>% kNN(k=5, imp_var = FALSE)
```

```{r}
write_parquet(data2004_f, "data/data2004_f.parquet")
write_parquet(data2004_i, "data/data2004_i.parquet")
```

# Résultats descriptifs

```{r}
# Items used by B&M
q2_vars <- c('clseusa')
q3_vars <- c('ambornin', 'amcit', 'amlived', 'amenglsh', 'amchrstn', 'amgovt', 'amfeel')
q4_vars <- c('amcitizn', 'amshamed', 'belikeus', 'ambetter', 'ifwrong')
q5_vars = c('proudsss', 'proudgrp', 'proudpol', 'prouddem', 'proudeco', 'proudspt', 'proudart', 'proudhis', 'proudmil', 'proudsci')

# All items
# q2_vars <- c('clsetown', 'clsestat', 'clseusa', 'clsenoam')
# q3_vars <- c(q3_vars, 'amancstr')
# q4_vars <- c(q4_vars, 'amsports', 'lessprd') # with all items

q2_vars_f <- paste0(q2_vars, "_f")
q3_vars_f <- paste0(q3_vars, "_f")
q4_vars_f <- paste0(q4_vars, "_f")
q5_vars_f <- paste0(q5_vars, "_f")

q2_vars_n <- paste0(q2_vars, "_n")
q3_vars_n <- paste0(q3_vars, "_n")
q4_vars_n <- paste0(q4_vars, "_n")
q5_vars_n <- paste0(q5_vars, "_n")

f_outcomes <- c(q2_vars_f, q3_vars_f, q4_vars_f, q5_vars_f)
n_outcomes <- c(q2_vars_n, q3_vars_n, q4_vars_n, q5_vars_n)
```

## Outcomes

```{r}
likert_table <- 
  list(
    data2004_i %>% tbl_likert(include = all_of(f_outcomes)),
    tbl_wide_summary(
      data2004_i|> mutate(across(all_of(f_outcomes), \(x) unclass(x))),
      statistic = c("{mean}", "{sd}", "{N_nonmiss}"),
      type = ~ "continuous",
      include = all_of(f_outcomes),
      digits = ~ 1)) %>%
  tbl_merge(tab_spanner = FALSE) %>%
  as_gt(rownames_to_stub = TRUE) %>%
  
  # Shortening of labels
  fmt(columns = "label", fns = function(x) {
    str_to_sentence( # Capitalize first letter
      str_remove(x, "^How (close|important|proud) \\.\\.\\.") # Remove first characters
    )}) %>%
  fmt(columns = "stat_3_2", fns = function(x) str_sub(x, 1, -3)) %>%

  # Grouping of questions
  tab_row_group(label = "How close do you feel to?", rows = which(.data$variable %in% q2_vars_f), id = "close") %>%
  tab_row_group(label = "How important do you think each of the following is?", rows = which(.data$variable %in% q3_vars_f), id = "imp") %>%
  tab_row_group(label = "How much do you agree or disagree with the following statements?", rows = which(.data$variable %in% q4_vars_f), id = "agree") %>%
  tab_row_group(label = "How proud are you of America in each of the following?", rows = which(.data$variable %in% q5_vars_f), id = "proud") %>%
  row_group_order(c("close", "imp", "agree", "proud")) %>%

  # Styling  
  tab_style(
    style = list(
      cell_fill(color = "lightgrey"),
      cell_text(style = "italic", weight = "bold")),
    location = cells_row_groups())  %>%
  tab_style(
    style = cell_borders(sides = "left", style = "dashed", color = "black"),
    locations = list(
      cells_column_labels(columns = "stat_1_1" | "stat_1_2" | "stat_3_2"),
      cells_body(columns = "stat_1_1" | "stat_1_2" | "stat_3_2")))

likert_table
```

```{r include=FALSE}
plot <- gglikert(data2004_f,
                 include = all_of(f_outcomes),
                 sort = "ascending") +
  scale_fill_brewer(palette = "RdYlBu")

ggsave("output/desc/likert_plot_2004.png", plot = plot, width = 10, height = 8, dpi = 300)
```

```{r include=FALSE}
# Creating likert plots for each question
p1 <- gglikert(data2004_f, include = all_of(q2_vars_f), sort = "ascending", add_totals = FALSE) +
  scale_x_continuous(labels = function(x) abs(x)*100, limits = c(-0.51, 1)) + 
  scale_fill_brewer(palette = "RdYlBu") + 
  ggtitle("How close do you feel to?") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))

p2 <- gglikert(data2004_f, include = all_of(q3_vars_f), sort = "ascending", add_totals = FALSE) +
  scale_x_continuous(labels = function(x) abs(x)*100, limits = c(-0.51, 1)) + 
  scale_fill_brewer(palette = "RdYlBu") +
  ggtitle("How important do you think each of the following is?") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))

p3 <- gglikert(data2004_f, include = all_of(q5_vars_f), sort = "ascending", add_totals = FALSE) + 
  scale_fill_brewer(palette = "RdYlBu") +
  scale_x_continuous(labels = function(x) abs(x)*100, limits = c(-0.51, 1)) +
  ggtitle("How proud are you of America in each of the following?") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))

p4 <- gglikert(data2004_f, include = all_of(q4_vars_f), sort = "ascending", add_totals = FALSE) + 
  scale_fill_brewer(palette = "RdYlBu") +
  scale_x_continuous(labels = function(x) abs(x)*100, limits = c(-0.51, 1)) +
  ggtitle("How much do you agree or disagree with the following statements?") +
  theme(plot.title = element_text(hjust = 0.5))

# Stacking the plots while controlling for their relative height
plot <- grid.arrange(p1, p2, p3, p4, ncol = 1, heights = c(
  max(0.22, length(q2_vars_f)*0.11), 
  length(q3_vars_f)*0.11, 
  length(q5_vars_f)*0.10, 
  length(q4_vars_f)*0.13))

# Adding a title
title <- textGrob("Likert 2004", gp = gpar(fontsize = 16, fontface = "bold"))
plot <- gtable_add_rows(plot, unit(1, "cm"), pos = 0)
plot <- gtable_add_grob(plot, title, t = 1, l = 1, r = ncol(plot))

ggsave("output/desc/likert_plots_2004.png", plot = plot, width = 10, height = 15, dpi = 300)
```

## Contrôles

# ACP

Il faut bien décider / justifier de scaler ou pas (scale.unit = TRUE / FALSE). 

- Sans scaling : 2 axes, portant 26 et 13 % de l'inertie totale, dont l'opposition est essentiellement tirée par 3 variables (amchrstn, ambornin, amlived) 

- Avec scaling : 2 axes, potant 26 et 11% de l'inertie totale, dont l'opposition est tirée par une quinzaine de variables (dont les précédentes, dont l'effet est en quelque sorte dilué)

```{r}
f_controls <- c('sex', 'race_f', 'born_usa', 'party_fs', 'religstr_f', 'reltrad_f', 'region_f', 'realinc_f')

pca_data <- data2004_i %>%
  select(all_of(c(n_outcomes, f_controls))) %>%
  rename_with(~ str_remove(., "_n$")) # Remove _n from variables names for cleaner outputs

pca_results <- PCA(pca_data, scale.unit = TRUE, quali.sup = f_controls, ncp = 10, graph = FALSE)
```

```{r}
# Fonction pour tracer les corrplots
draw_corrplot <- function(data, title, subtitle, filename, range) {
  corrplot <- ggcorrplot(
    data,
    method = "square",
    ggtheme = theme_grey,
    show.legend = TRUE,
    outline.color = "#636363",
    tl.cex = 8) +
    
    if (identical(range, c(-1,1))) {
      scale_fill_gradient2(limit = c(-1,1), 
                           low = "#6D9EC1", 
                           mid = "white", 
                           high =  "#E46726", 
                           midpoint = 0, 
                           oob = scales::oob_squish)}
  else if (identical(range, c(0,1))) {
    scale_fill_gradient2(limit = c(0, 1), 
                         low = "white", 
                         high = "#E46726", 
                         oob = scales::oob_squish)}
  
  corrplot <- corrplot + theme(
    legend.title = element_blank(),
    legend.key.width = unit(0.3, "cm"),
    legend.key.height = unit(1, "null"))
    
  # On ajoute titres et sous-titres pour les graphs affichés
  corrplot <- corrplot + 
    ggtitle(title) +
    theme(plot.title = element_text(hjust = 0.5, size = 12))
  
  if (subtitle != "") {
    corrplot <- corrplot + 
      labs(subtitle = subtitle) + 
      theme(plot.subtitle = element_text(hjust = 0.5, size = 12))
  }
  
  ggsave(filename, plot = corrplot)
  
  print(corrplot)
}
```

```{r}
# Résultats
## Histogramme de la contribution des axes à la variance totale
screeplot <- fviz_screeplot(pca_results, addlabels = TRUE, ylim = c(0, 45), title = "") + theme_gray()
screeplot$layers[[1]]$aes_params$fill <- "lightskyblue"
screeplot$layers[[1]]$aes_params$colour <- "cornflowerblue"
screeplot$layers[[2]]$aes_params$colour <- "darkblue"
screeplot$layers[[3]]$aes_params$colour <- "darkblue"
screeplot$layers[[4]]$aes_params$colour <- "darkblue"
screeplot$labels$x <- "Dimensions"
screeplot$labels$y <- "% de variance expliquée"
screeplot$labels$title = "Histogramme de l'inertie totale"
screeplot$theme$plot.title$hjust <- 0.5
screeplot
ggsave("output/acp/screeplot.png", plot = screeplot, width = 10, height = 6, units = "in", dpi = 300)

## Contribution des variables aux axes
## Correspond à la qualité de représentation des variables (= cos2) normalisée entre 1 et 100
## Présentable à l'aide d'un tableau...
coeffs <- pca_results$var$contrib
labels <- rownames(pca_results$var$contrib)
axis_df <- data.frame(labels, coeffs, row.names = NULL)
colnames(axis_df) <- c("Variables", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10")
axis_tbl <- axis_df %>%
  gt() %>%
  fmt_number(decimals = 2, drop_trailing_zeros = TRUE) %>%
  tab_header("Contribution des variables à l'inertie des axes", subtitle = NULL, preheader = NULL) %>%
  tab_spanner(label = "Axes", columns = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"), id = "axes") %>%
  data_color(method = "numeric", columns = !matches("Variables"), palette ="Oranges", direction = "column") %>%
  tab_row_group(label = "How close do you feel to?", rows = which(.data$Variables %in% q2_vars), id = "close") %>%
  tab_row_group(label = "How important do you think each of the following is?", rows = which(.data$Variables %in% q3_vars), id = "imp") %>%
  tab_row_group(label = "How much do you agree or disagree with the following statements?", rows = which(.data$Variables %in% q4_vars), id = "agree") %>%
  tab_row_group(label = "How proud are you of America in each of the following?", rows = which(.data$Variables %in% q5_vars), id = "proud") %>%
  row_group_order(c("close", "imp", "agree", "proud")) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = list(
      cells_column_labels(columns = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")),
      cells_body(columns = !matches("Variables")))) %>%
  tab_style(
    style = cell_fill(color = "lightgrey"),
    locations = cells_column_labels(columns = c("1", "3", "5", "7", "9"))) 
axis_tbl
gtsave(axis_tbl, filename = "contrib_axes.docx", path = "output/acp/")

## ... d'un corrplot ...
draw_corrplot(t(pca_results$var$contrib[, 1:10]/100), "Contribution des variables à l'inertie des axes", "", "output/acp/contrib_axes.png", range = c(0,1))

## ... ou de graphs
contrib_1 <- fviz_contrib(pca_results, choice = "var", axes = 1, top = 10)
contrib_1$layers[[1]]$aes_params$fill <- "lightskyblue"
contrib_1$layers[[1]]$aes_params$colour <- "cornflowerblue"
contrib_1$layers[[2]]$aes_params$colour <- "darkblue"
contrib_1$labels$title <- "Contribution des variables à l'axe 1"
contrib_1$theme$plot.title$hjust <- 0.5
contrib_1
ggsave("output/acp/contrib_axe_1.png", plot = contrib_1)

contrib_2 <- fviz_contrib(pca_results, choice = "var", axes = 2, top = 10)
contrib_2$layers[[1]]$aes_params$fill <- "lightskyblue"
contrib_2$layers[[1]]$aes_params$colour <- "cornflowerblue"
contrib_2$layers[[2]]$aes_params$colour <- "darkblue"
contrib_2$labels$title <- "Contribution des variables à l'axe 2"
contrib_2$theme$plot.title$hjust <- 0.5
contrib_2
ggsave("output/acp/contrib_axe_2.png", plot = contrib_2)

## Corrélation des variables aux axes
## Avec à nouveau deux représentations possibles...
## Des corrplots
draw_corrplot(t(pca_results$var$coord[, 1:5]), title = "Corrélation des outcomes aux axes", "", "output/acp/corr_outc_axes.png", range = c(-1,1))
draw_corrplot(t(pca_results$quali.sup$coord[, 1:5]), "Corrélation des régresseurs", "aux axes", "output/acp/corr_rég_axes.png", range = c(-1,1))
## Des projections sur les plans factoriels
proj_var <- fviz_pca_var(pca_results, 
             axes = c(1, 2),
             select.var = list(contrib = 12),
             col.circle = '#636363',
             col.var = "contrib",
             gradient.cols = c("cornflowerblue", "#E46726"),
             title = "Projection des variables sur les axes 1 et 2", 
             repel = TRUE) + 
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5))
proj_var$layers <- proj_var$layers[-c(4, 5)] # removing original hline and vline
proj_var <- proj_var +
  geom_hline(yintercept = 0, color = "#636363", alpha = 0.5, linetype = "twodash") +
  geom_vline(xintercept = 0, color = "#636363", alpha = 0.5, linetype = "twodash")
proj_var
ggsave("output/acp/proj_var.png", plot = proj_var)

proj_ind <- fviz_pca_ind(pca_results, 
             axes = c(1, 2),
             habillage = "party_fs",
             pointshape = 16,
             alpha.ind = 0.7,
             title = "Projection des individus sur les axes 1 et 2", 
             label = "none",
             repel = TRUE) +
  theme_gray() +
  scale_color_manual(
    name = "Affiliation\npartisane",
    values = c("Republican" = "coral1", "Independent" = "lightgreen", "Democrat" = "cornflowerblue"),
    labels = c("Republican" = "Republicains", "Independent" = "Indépendants", "Democrat" = "Démocrates")) +
  theme(plot.title = element_text(hjust = 0.5))
proj_ind$layers <- proj_ind$layers[-c(2, 3)] # removing original hline and vline
proj_ind <- proj_ind +
  geom_hline(yintercept = 0, color = "#636363", linetype = "twodash") +
  geom_vline(xintercept = 0, color = "#636363", linetype = "twodash")
proj_ind
ggsave("output/acp/proj_ind.png", plot = proj_ind)

proj_ind <- proj_ind + xlim(-3, 3) + ylim(-3, 3) # Zoom in
ggsave("output/acp/proj_ind_zoom.png", plot = proj_ind)

## Qualité de représentation des variables
draw_corrplot(t(pca_results$var$cos2[, 1:5]), "Qualité de représentation", "des outcomes", "output/acp/qual_rep_outc.png", range = c(0,1))
draw_corrplot(t(pca_results$quali.sup$cos2[, 1:5]), "Qualité de représentation", "des régresseurs", "output/acp/qual_rep_régr.png", range = c(0,1))
```

# kmeans

https://www.datanovia.com/en/blog/types-of-clustering-methods-overview-and-quick-start-r-code/
https://bookdown.org/evraloui/lbira2110/clustering.html

FUNcluster 	= a partitioning function which accepts as first argument a (data) matrix like x, second argument, say k, k >= 2, the number of clusters desired, and returns a list with a component named cluster which contains the grouping of observations. Allowed values include: 
kmeans, 
cluster::pam, 
cluster::clara, 
cluster::fanny, # Fuzzy kmeans
cluster::hcut, # Classification ascendante hiérarchique
etc.

```{r eval=FALSE}
data_km <- data2004_i %>% select(n_outcomes) %>% na.omit() %>% scale()

fviz_nbclust(data_km, 
             FUNcluster = cluster::pam, 
             method = "gap_stat") +
  theme(plot.title = element_text(hjust = 0.5))

fviz_nbclust(data_km, 
             FUNcluster = cluster::pam, 
             method='silhouette') +
  theme(plot.title = element_text(hjust = 0.5))

fviz_nbclust(data_km, 
             FUNcluster = cluster::pam, 
             method='wss') +
  theme(plot.title = element_text(hjust = 0.5))

results_km <- cluster::pam(data_km, 2, nstart = 25)
results_km <- kmeans(data_km, 4, nstart = 25)

fviz_cluster(results_km, 
             data = data_km,
             labelsize = 0,
             palette = c("#00AFBB", "#2E9FDF", "#E7B800", "#FC4E07"),
             ggtheme = theme_minimal(),
             main = "Partitioning Clustering Plot") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

# DBScan

```{r}
library("fpc")
db_results <- fpc::dbscan(data_km, eps = 4, MinPts = 5)

fviz_cluster(db_results,
             data = data_km,
             stand = FALSE,
             ellipse = TRUE,
             show.clust.cent = TRUE,
             geom = "point",
             palette = "jco")

print(db_results)

print(paste("Number of clusters:", length(unique(db_results$cluster[db_results$cluster != 0]))))
print(paste("Number of noise points:", sum(db_results$cluster == 0)))
```

```{r}
library(tidySEM)
lpa.data <- data2004_i %>% select(all_of(n_outcomes))
lpa.res <- mx_profiles(data = lpa.data, classes = 4)
fit <- table_fit(lpa.res)

fit %>%
  select(Classes, LL, Parameters, AIC, BIC) %>%
  gt() %>%
  fmt_number(c(LL, AIC, BIC), decimals = 1) %>%
  tab_style(
    style = cell_fill(
      color = "lightgreen",
      alpha = 0.7),
    locations = cells_body(
      columns = AIC,
      rows = AIC == min(AIC, na.rm = TRUE))) %>%
  tab_style(
    style = cell_fill(
      color = "lightgreen",
      alpha = 0.7),
    locations = cells_body(
      columns = BIC,
      rows = BIC == min(BIC, na.rm = TRUE))) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold", style = "italic"),
      cell_text(align = "center")),
    locations = cells_column_labels(everything())) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body())

predict.probs <- class_prob(lpa.res)
predict.probs$sum.posterior %>%
  gt() %>%
  fmt_number(count, decimals = 0) %>%
  fmt_number(proportion, decimals = 3) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold", style = "italic"),
      cell_text(align = "center")),
    locations = cells_column_labels(everything()))

mg_probs <-
  rbind(
    lpa.res$output$matrices$class1.M,
    lpa.res$output$matrices$class2.M) %>%
  as.data.frame() %>%
  mutate(class = row_number()) %>%
  setNames(c(outcomes, "p.class")) %>%
  pivot_longer(
    cols = -p.class,
    names_to = "Column",
    values_to = "Value") %>%
  pivot_wider(
    names_from = p.class,
    values_from = Value) %>%
  rename(
    Outcome = "Column",
    "Class 1" = "1",
    "Class 2" = "2") %>%
  gt() %>%
  fmt_number(decimals = 1) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold", style = "italic"),
      cell_text(align = "center")),
    locations = cells_column_labels(everything()))
mg_probs

plot_profiles(lpa.res)
```

